Figures from: Vertebrate host availability and the thermal properties of mosquito-borne parasite transmission

### 2023-06-09 manuscript-figures.Rmd
add "half" violin plots to show CT distributions
- need to get rid of old code for previous figures

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, cache = FALSE, warning = FALSE, fig.pos = "H",
  out.extra = ""
)
# Load Libraries----------------------------------------------------------------
library(tidyverse)
library(latex2exp)
library(reshape2)
library(cowplot)
library(viridis)
library(RColorBrewer)
library(MetBrewer)
library(here)
library(lemon)
library(zplyr) # from https://github.com/burchill/zplyr/ # only needed for placing text using absolute coordinates in contact comparison figure

@@

CTmin_heat_plots <- CTmin_df %>%
  select(-median) %>% 
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = width of parasite thermal median_CTwidth
  ggplot(aes(x = KH, y = sigmaH_proxy, z = median_proxy)) +
  # CTmin for FINITE sigmaH:
  geom_contour_filled(
    data = filter(CTmin_df, 
                  sigmaH_proxy < 10^2.2),
    breaks = CTmin_breaks
    ) +
  # CTmin for INFINITE sigmaH:
  geom_contour_filled(
    data = filter(CTmin_df,
                  sigmaH_proxy > 10^2.4,
                  sigmaH_proxy < infinite_divide),
    breaks = CTmin_breaks
    ) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +
  # fill:
    scale_fill_manual(
    name = "Critical thermal minimum (°C)",
    values = c(viridis(9), "grey", "grey"),
    labels = ~ ifelse(.x < maxCTmin, .x, 'n/a')
  ) +
  # faceting:
  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
  # legend:
  guides(fill = guide_coloursteps(
    title.position = "top",
    title.hjust = 0.5,
    barwidth = unit(7, "cm"),
    show.limits = TRUE
  )) +
  # theme options:
  theme_minimal() +
  theme(
    legend.box = "horizontal",
    legend.position = "bottom",
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.direction = "horizontal",
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

@@

CTmax_heat_plots <- CTmax_df %>%
  select(-median) %>% 
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = width of parasite thermal median_CTwidth
  ggplot(aes(x = KH, y = sigmaH_proxy, z = median_proxy)) +
  # CTmin for FINITE sigmaH:
  geom_contour_filled(
    data = filter(CTmax_df, 
                  sigmaH_proxy < 10^2.2),
    breaks = CTmax_breaks
    ) +
  # CTmin for INFINITE sigmaH:
  geom_contour_filled(
    data = filter(CTmax_df,
                  sigmaH_proxy > 10^2.4,
                  sigmaH_proxy < infinite_divide),
    breaks = CTmax_breaks
    ) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +
  # fill:
    scale_fill_manual(
    name = "Critical thermal maximum (°C)",
    values = c("grey", viridis(9)),
    labels = ~ ifelse(.x < minCTmax-1, 'n/a', .x)
  ) +
  # faceting:
  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
  # legend:
  guides(fill = guide_coloursteps(
    title.position = "top",
    title.hjust = 0.5,
    barwidth = unit(7, "cm"),
    show.limits = TRUE
  )) +
  # theme options:
  theme_minimal() +
  theme(
    legend.box = "horizontal",
    legend.position = "bottom",
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.direction = "horizontal",
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

@@

### Option 1: inline violin plots ----
plot.densities_violin_inline <- ggplot() +
  geom_violin(
    data = filter(all.density.df, variable == "Thermal optimum"),
    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "Topt")
  ) +
  geom_violin(
    data = filter(all.density.df, variable == "Critical thermal minimum"),
    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmin"),
  ) +
  geom_violin(
    data = filter(all.density.df, variable == "Critical thermal maximum"),
    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmax"),
  ) +
  scale_x_continuous(
    name = "Temperature (°C)",
    expand = c(0, 0)
  ) +
  scale_y_discrete(
    name = "Vertebrate host population density (ind/ha)"
  ) +
  scale_linetype(
    name = "Biting tolerance\n(bites per host per day)"
  ) +
  scale_fill_discrete(
    name = "",
    breaks = c("CTmin", "Topt", "CTmax"),
    labels = c("Critical thermal minimum", "Thermal optimum", "Critical thermal maximum")
  ) +
  facet_wrap(~system_label, labeller = labeller()) +
  theme_minimal_grid() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )
shift_legend(plot.densities_violin_inline)

### Option 2: inline box and whisker plots ----
plot.densities_boxwhisker_inline <- ggplot() +
  geom_boxplot(
    data = filter(all.density.df, variable == "Thermal optimum"),
    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "Topt")
  ) +
  geom_boxplot(
    data = filter(all.density.df, variable == "Critical thermal minimum"),
    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmin"),
  ) +
  geom_boxplot(
    data = filter(all.density.df, variable == "Critical thermal maximum"),
    aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmax"),
  ) +
  scale_x_continuous(
    name = "Temperature (°C)",
    expand = c(0, 0)
  ) +
  scale_y_discrete(
    name = "Vertebrate host population density (ind/ha)"
  ) +
  scale_linetype(
    name = "Biting tolerance\n(bites per host per day)"
  ) +
  scale_fill_discrete(
    name = "",
    breaks = c("CTmin", "Topt", "CTmax"),
    labels = c("Critical thermal minimum", "Thermal optimum", "Critical thermal maximum")
  ) +
  facet_wrap(~system_label, labeller = labeller()) +
  theme_minimal_grid() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )
shift_legend(plot.densities_boxwhisker_inline)

### Option 3: stacked violin plots ----
plot.densities_violin_stacked <- ggplot() +
  geom_violin(
    data = all.density.df,
    aes(x = value, y = KH_factor, fill = variable, linetype = sigmaH)
  ) +
  scale_x_continuous(
    name = "Temperature (°C)",
    expand = c(0, 0)
  ) +
  scale_y_discrete(
    name = "Vertebrate host population density (ind/ha)"
  ) +
  scale_linetype(
    name = "Biting tolerance\n(bites per host per day)"
  ) +
  scale_fill_discrete(
    name = ""
  ) +
  facet_wrap(~system_label, labeller = labeller()) +
  theme_minimal_grid() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )
shift_legend(plot.densities_violin_stacked)

### Option 4: stacked box and whisker plots ----
plot.densities_boxwhisker_stacked <- ggplot() +
  geom_boxplot(
    data = all.density.df,
    aes(x = value, y = KH_factor, fill = variable, linetype = sigmaH)
  ) +
  scale_x_continuous(
    name = "Temperature (°C)",
    expand = c(0, 0)
  ) +
  scale_y_discrete(
    name = "Vertebrate host population density (ind/ha)"
  ) +
  scale_linetype(
    name = "Biting tolerance\n(bites per host per day)"
  ) +
  scale_fill_discrete(
    name = ""
  ) +
  facet_wrap(~system_label, labeller = labeller()) +
  theme_minimal_grid() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )
shift_legend(plot.densities_boxwhisker_stacked)
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE, cache = FALSE, warning = FALSE, fig.pos = "H",
  out.extra = ""
)
# Load Libraries----------------------------------------------------------------
library(tidyverse)
library(latex2exp)
library(reshape2)
library(cowplot)
library(viridis)
library(RColorBrewer)
library(MetBrewer)
library(here)
library(lemon)
library(see) # for half-violin plots
library(zplyr) # from https://github.com/burchill/zplyr/ # only needed for placing text using absolute coordinates in contact comparison figure

@@

CTmin_heat_plots <- CTmin_df %>%
  select(-median) %>% 
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = width of parasite thermal median_CTwidth
  ggplot(aes(x = KH, y = sigmaH_proxy, z = median_proxy)) +
  # CTmin for FINITE sigmaH:
  geom_contour_filled(
    data = filter(CTmin_df, 
                  sigmaH_proxy < 10^2.2),
    breaks = CTmin_breaks
    ) +
  # CTmin for INFINITE sigmaH:
  geom_contour_filled(
    data = filter(CTmin_df,
                  sigmaH_proxy > 10^2.4,
                  sigmaH_proxy < infinite_divide),
    breaks = CTmin_breaks
    ) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +
  # fill:
    scale_fill_manual(
    name = "Critical thermal minimum (°C)",
    values = c(viridis(9), "grey", "grey"),
    labels = ~ ifelse(.x < maxCTmin, .x, 'n/a')
  ) +
  # faceting:
  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
  # legend:
  guides(fill = guide_coloursteps(
    title.position = "top",
    title.hjust = 0.5,
    barwidth = 12,
    show.limits = TRUE
  )) +
  # theme options:
  theme_minimal() +
  theme(
    legend.box = "horizontal",
    legend.position = "bottom",
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.direction = "horizontal",
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

@@

CTmax_heat_plots <- CTmax_df %>%
  select(-median) %>% 
  ## Set up plot ##
  # x = biting tolerance (with a point at infinity),
  # y = vertebrate host population density,
  # color = width of parasite thermal median_CTwidth
  ggplot(aes(x = KH, y = sigmaH_proxy, z = median_proxy)) +
  # CTmin for FINITE sigmaH:
  geom_contour_filled(
    data = filter(CTmax_df, 
                  sigmaH_proxy < 10^2.2),
    breaks = CTmax_breaks
    ) +
  # CTmin for INFINITE sigmaH:
  geom_contour_filled(
    data = filter(CTmax_df,
                  sigmaH_proxy > 10^2.4,
                  sigmaH_proxy < infinite_divide),
    breaks = CTmax_breaks
    ) +
  # x-axis: log10-scale with no buffer space
  scale_x_log10(
    name = TeX("Vertebrate host population density (ind/ha)"),
    expand = c(0, 0),
    limits = c(0.05, 1E4),
    breaks = 10^seq(-1, 4, 1),
    labels = TeX(c("$0.1$", "$1$", "$10", "$100$", "$10^3$", "$10^4$"))
  ) +
  # y-axis: log10-scale y axis, with no buffer space
  scale_y_log10(
    name = TeX("Biting tolerance (bites per host per day)"),
    expand = c(0, 0),
    breaks = sigmaH_breaks,
    labels = sigmaH_labels
  ) +
  # fill:
    scale_fill_manual(
    name = "Critical thermal maximum (°C)",
    values = c("grey", viridis(9)),
    labels = ~ ifelse(.x < minCTmax-1, 'n/a', .x)
  ) +
  # faceting:
  facet_wrap(~system_label, scales = "free", nrow = 2, labeller = labeller()) +
  # legend:
  guides(fill = guide_coloursteps(
    title.position = "top",
    title.hjust = 0.5,
    barwidth = 12,
    show.limits = TRUE
  )) +
  # theme options:
  theme_minimal() +
  theme(
    legend.box = "horizontal",
    legend.position = "bottom",
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    legend.direction = "horizontal",
    legend.justification = "left",
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  )

@@

### Option 1: inline violin plots ----
plot.densities_violin_inline <- ggplot() +
  # CT min 
  geom_violinhalf(
    data = filter(all.density.df, variable == "Critical thermal minimum",
                  sigmaH == 100),
    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmin"),
    lwd = 1
  ) +
  geom_violinhalf(
    data = filter(all.density.df, variable == "Critical thermal minimum",
                  sigmaH == Inf),
    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmin"),
    lwd = 1,
    flip = TRUE
  ) +
  # CT max 
  geom_violinhalf(
    data = filter(all.density.df, variable == "Critical thermal maximum",
                  sigmaH == 100),
    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmax"),
    lwd = 1
  ) +
  geom_violinhalf(
    data = filter(all.density.df, variable == "Critical thermal maximum",
                  sigmaH == Inf),
    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "CTmax"),
    lwd = 1,
    flip = TRUE
  ) +
  # Thermal optima
  geom_violinhalf(
    data = filter(all.density.df, variable == "Thermal optimum",
                  sigmaH == 100),
    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "Topt"),
    lwd = 1
  ) +
  geom_violinhalf(
    data = filter(all.density.df, variable == "Thermal optimum",
                  sigmaH == Inf),
    aes(y = value, x = KH_factor, linetype = sigmaH, fill = "Topt"),
    lwd = 1,
    flip = TRUE
  ) +
  scale_x_discrete(
    name = "Vertebrate host population density (ind/ha)"
  ) +
  scale_y_continuous(
    name = "Temperature (°C)",
    expand = c(0, 0)
  ) +
  scale_linetype(
    name = "Biting tolerance\n(bites per host per day)"
  ) +
  scale_fill_discrete(
    name = "",
    breaks = c("CTmin", "Topt", "CTmax"),
    labels = c("Critical thermal minimum", "Thermal optimum", "Critical thermal maximum")
  ) +
  facet_wrap(~system_label, labeller = labeller()) +
  theme_minimal_grid() +
  theme(
    legend.margin = margin(0, 0, 0, 0),
    legend.title = element_text(size = 10),
    axis.title.x = element_text(hjust = 0.5),
    strip.text = ggtext::element_markdown(
      size = 11,
      hjust = 0,
      padding = margin(0, 0, 0, 0),
      margin = margin(1, 1, 1, 1)
    )
  ) +
  coord_flip()
shift_legend(plot.densities_violin_inline)
```

<!-- ### Option 2: inline box and whisker plots ---- -->
<!-- plot.densities_boxwhisker_inline <- ggplot() + -->
<!--   geom_boxplot( -->
<!--     data = filter(all.density.df, variable == "Thermal optimum"), -->
<!--     aes(x = value, y = KH_factor, linetype = sigmaH, fill = "Topt") -->
<!--   ) + -->
<!--   geom_boxplot( -->
<!--     data = filter(all.density.df, variable == "Critical thermal minimum"), -->
<!--     aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmin"), -->
<!--   ) + -->
<!--   geom_boxplot( -->
<!--     data = filter(all.density.df, variable == "Critical thermal maximum"), -->
<!--     aes(x = value, y = KH_factor, linetype = sigmaH, fill = "CTmax"), -->
<!--   ) + -->
<!--   scale_x_continuous( -->
<!--     name = "Temperature (°C)", -->
<!--     expand = c(0, 0) -->
<!--   ) + -->
<!--   scale_y_discrete( -->
<!--     name = "Vertebrate host population density (ind/ha)" -->
<!--   ) + -->
<!--   scale_linetype( -->
<!--     name = "Biting tolerance\n(bites per host per day)" -->
<!--   ) + -->
<!--   scale_fill_discrete( -->
<!--     name = "", -->
<!--     breaks = c("CTmin", "Topt", "CTmax"), -->
<!--     labels = c("Critical thermal minimum", "Thermal optimum", "Critical thermal maximum") -->
<!--   ) + -->
<!--   facet_wrap(~system_label, labeller = labeller()) + -->
<!--   theme_minimal_grid() + -->
<!--   theme( -->
<!--     legend.margin = margin(0, 0, 0, 0), -->
<!--     legend.title = element_text(size = 10), -->
<!--     axis.title.x = element_text(hjust = 0.5), -->
<!--     strip.text = ggtext::element_markdown( -->
<!--       size = 11, -->
<!--       hjust = 0, -->
<!--       padding = margin(0, 0, 0, 0), -->
<!--       margin = margin(1, 1, 1, 1) -->
<!--     ) -->
<!--   ) -->
<!-- shift_legend(plot.densities_boxwhisker_inline) -->

<!-- ### Option 3: stacked violin plots ---- -->
<!-- plot.densities_violin_stacked <- ggplot() + -->
<!--   geom_violin( -->
<!--     data = all.density.df, -->
<!--     aes(x = value, y = KH_factor, fill = variable, linetype = sigmaH) -->
<!--   ) + -->
<!--   scale_x_continuous( -->
<!--     name = "Temperature (°C)", -->
<!--     expand = c(0, 0) -->
<!--   ) + -->
<!--   scale_y_discrete( -->
<!--     name = "Vertebrate host population density (ind/ha)" -->
<!--   ) + -->
<!--   scale_linetype( -->
<!--     name = "Biting tolerance\n(bites per host per day)" -->
<!--   ) + -->
<!--   scale_fill_discrete( -->
<!--     name = "" -->
<!--   ) + -->
<!--   facet_wrap(~system_label, labeller = labeller()) + -->
<!--   theme_minimal_grid() + -->
<!--   theme( -->
<!--     legend.margin = margin(0, 0, 0, 0), -->
<!--     legend.title = element_text(size = 10), -->
<!--     axis.title.x = element_text(hjust = 0.5), -->
<!--     strip.text = ggtext::element_markdown( -->
<!--       size = 11, -->
<!--       hjust = 0, -->
<!--       padding = margin(0, 0, 0, 0), -->
<!--       margin = margin(1, 1, 1, 1) -->
<!--     ) -->
<!--   ) -->
<!-- shift_legend(plot.densities_violin_stacked) -->

<!-- ### Option 4: stacked box and whisker plots ---- -->
<!-- plot.densities_boxwhisker_stacked <- ggplot() + -->
<!--   geom_boxplot( -->
<!--     data = all.density.df, -->
<!--     aes(x = value, y = KH_factor, fill = variable, linetype = sigmaH) -->
<!--   ) + -->
<!--   scale_x_continuous( -->
<!--     name = "Temperature (°C)", -->
<!--     expand = c(0, 0) -->
<!--   ) + -->
<!--   scale_y_discrete( -->
<!--     name = "Vertebrate host population density (ind/ha)" -->
<!--   ) + -->
<!--   scale_linetype( -->
<!--     name = "Biting tolerance\n(bites per host per day)" -->
<!--   ) + -->
<!--   scale_fill_discrete( -->
<!--     name = "" -->
<!--   ) + -->
<!--   facet_wrap(~system_label, labeller = labeller()) + -->
<!--   theme_minimal_grid() + -->
<!--   theme( -->
<!--     legend.margin = margin(0, 0, 0, 0), -->
<!--     legend.title = element_text(size = 10), -->
<!--     axis.title.x = element_text(hjust = 0.5), -->
<!--     strip.text = ggtext::element_markdown( -->
<!--       size = 11, -->
<!--       hjust = 0, -->
<!--       padding = margin(0, 0, 0, 0), -->
<!--       margin = margin(1, 1, 1, 1) -->
<!--     ) -->
<!--   ) -->
<!-- shift_legend(plot.densities_boxwhisker_stacked) -->
<!-- ``` -->
